Draft Thesis Proposal

### 2019-09-09 ThesisProposal.Rmd
more lit with some quotes

@buur18

@@

>>>>

“There is no clear-cut method for determining when the MICE algorithm has converged” (@buur18, \textsection 6.5).

“Convergence is diagnosed when the variance between different sequences is no larger than the variance within each individual sequence” (@buur18, \textsection 6.5).

“Several expository reviews are available that assess convergence diagnostics for MCMC methods (Cowles and Carlin 1996; Brooks and Gelman 1998; El Adlouni, Favre, and Bobée 2006). Cowles and Carlin (1996) conclude that “automated convergence monitoring (as by a machine) is unsafe and should be avoided.” No method works best in all circumstances. The consensus is to assess convergence with a combination of tools. The added value of using a combination of convergence diagnostics for missing data imputation has not yet been systematically studied” (@buur18, \textsection 6.5).

@@

@scha02

@cowl96

"As MICE is an iterative procedure, it is important that convergence is achieved. This may be checked by computing, at each cycle, the means of imputed values and/or the values of regression coefficients, and seeing if they are stable" (@whit11, p. 394).
